\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage[top=2.3cm]{geometry}

\begin{document}
\sloppy

\title{\Huge\bfseries Line Route with All Distances Different}
\author{\Large Laureano Arcanio \quad \large (February 2026)}
\date{}
\maketitle
\section*{Problem}

Bob and Marley are observing a square field divided into $2025\times 2025$ unit plots arranged in rows and columns.
Each plot contains either a \emph{cat} or a \emph{dog}, arranged in a checkerboard pattern so that any two plots sharing a side contain different animals.

A \emph{trail} is a sequence of adjacent plots satisfying one of the following rules:
\begin{itemize}
\item the trail moves only to the right or downward, or
\item the trail moves only to the right or upward.
\end{itemize}

A trail is called \emph{balanced} if the number of cat-plots it visits differs from the number of dog-plots it visits by at most one.

Bob wants to cover the entire field with trails so that every plot belongs to exactly one trail and every trail is balanced.
Marley asks for the smallest possible number $M$ of trails needed.

\section*{Solution}

\subsection*{Step 1: Balance is automatic}

Along any allowed trail, each step moves to a neighboring plot.
Because the field is colored in a checkerboard pattern, each step switches the type of animal encountered.
Thus the animals along a trail strictly alternate.

If a trail contains an even number of plots, it visits the same number of cats and dogs.
If it contains an odd number of plots, the difference is exactly one.
Hence every allowed trail is automatically balanced, and the balance condition imposes no additional restriction.

Therefore, the problem reduces to determining the minimum number of allowed trails needed to cover all plots.

\subsection*{Step 2: An explicit construction}

Bob assigns one trail to each column of the field.
Each trail starts at the top plot of its column and proceeds straight downward through all $2025$ plots in that column.

These $2025$ trails:
\begin{itemize}
\item obey the movement rules,
\item are balanced by Step~1, and
\item together cover every plot exactly once.
\end{itemize}

Thus $M\le 2025$.

\subsection*{Step 3: Why fewer trails are impossible}

To show that Bob cannot do better, Marley argues as follows.

Each plot is divided along its diagonal from the upper-left corner to the lower-right corner, producing two triangular half-plots.
Think of these diagonals as mirrors.

Light beams are sent into the field through the midpoints of all boundary edges, perpendicular to the boundary.
There are exactly $4\cdot 2025$ such entry points.
Each beam reflects off the diagonal mirrors and eventually exits the boundary, thereby pairing the boundary edges into $2\cdot 2025$ disjoint pairs.

Consider how these beams interact with Bob’s trails.
Whenever a beam passes through a region corresponding to a segment of a trail, it exits that region on the same type of boundary edge (horizontal or vertical) on which it entered.
A beam can change from a horizontal boundary to a vertical boundary, or vice versa, only by passing through a triangular half-plot that is not paired with another half-plot by the trail structure.

Each trail has exactly two endpoints.
Each endpoint creates exactly one such unpaired half-plot.
Therefore the total number of unpaired half-plots is exactly $2M$.

On the other hand, among the $2\cdot 2025$ boundary pairs, at least $2025$ pairs must connect a horizontal boundary edge with a vertical boundary edge.
Each such mixed pair forces a beam to pass through at least one unpaired half-plot.

Hence
\[
2025 \le 2M.
\]

Repeating the same argument after shifting all beam entry points by half a unit along the boundary produces an independent pairing and yields the same inequality again.
Adding the two inequalities gives
\[
2\cdot 2025 \le 2M,
\]
so
\[
M\ge 2025.
\]

\subsection*{Conclusion}

Bob has exhibited a covering using $2025$ trails, and Marley has shown that no covering can use fewer.
Therefore the minimum possible number of trails is
\[
M=2025.
\]

\section*{Answer}

\[
\boxed{2025}
\]

\end{document}
